\documentclass[11pt,letterpaper,oneside,sans]{moderncv}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\moderncvtheme[black]{classic}


\firstname{Stanislas}
\familyname{Bach}
\title{V.I.E. at Adeneo Embedded}
\address{1000, 8th avenue}{Apt. 1-1202}{98104 Seattle}
\mobile{(206)-693-0316}
\email{sbach@adeneo-embedded.us}
\social[linkedin][www.linkedin.com/pub/stanislas-bach/63/6b5/431]{stanislas.bach}
\social[github]{sbach}
\extrainfo{23 years old - driver's license}
\quote{}


\begin{document}
\maketitle


\section{Education}

\cventry{2014}{%
  Bachelor
}{University of technology Belfort Montbéliard}{France}{}{%
  Computer Science
}

\cventry{2012}{%
  University Degree
}{University of technology Belfort Montbéliard}{France}{}{%
  Technology studies
}

\cventry{2010}{%
  European Baccalaureate
}{Lycée St-Ambroise, Chambéry}{France}{}{}


\section{Experience}

\cventry{Since August 2015}{%
  Intel's Xen GT integration
}{Adeneo Embedded, Bellevue, WA}{U.S.A}{}{%
  Development, integration \& testing of the Xen GT technology on the MinnowMax.
}

\cventry{February - August 2015}{%
  AM437x Android Kitkat BSP
}{Adeneo Embedded, Bellevue, WA}{U.S.A}{}{%
  Development of the internal B.S.P. and adaptation for the Rufus Cuff
  smartwatch, \newline e.g: WL18xx and PowerVR SGX integration with a Linux 3.14
  kernel.
}

\cventry{2015-2016}{%
  V.I.E. (12 months) at Adeneo Embedded
}{Bellevue, WA}{U.S.A}{}{%
  End-of-studies internship.
}

\cventry{Fall 2014}{%
  Design of a smartwatch
}{University of technology Belfort Montbéliard}{France}{}{%
  MSP430 based Bluetooth smartwatch as a research project.
}

\cventry{May 2014}{%
  WiFi positioning system
}{University of technology Belfort Montbéliard}{France}{}{%
  Indoor localization service using OpenWRT routers.
}

\cventry{September 2013}{%
  Internship (6 months) at Adeneo Embedded
}{Lyon}{France}{}{%
  Linux \& QNX BSP development and deployment on ARM platforms.
}

\cventry{Since 2012}{%
  Server Administration
}{}{}{}{%
  Installation, configuration, and maintenance of virtual private servers under
  Debian.
}

\cventry{September 2011}{%
  Design and construction of a quadcopter
}{}{}{}{%
  Frame, electronics, and real-time software for PC, Pocket Pc 2003, and
  Android.
}


\section{Computer skills}

\cvline{Languages}{%
  C/C++, Bash, Python, Assembly (ARM), VHDL, C\#, Java, PHP
}

\cvline{Analysis}{%
  Merise, UML
}

\cvline{Database}{%
  MySQL, Sqlite
}

\cvline{Operating systems}{%
  Linux (Arch, Debian, OpenWRT), Android, Pocket Pc, Windows
}

\cvline{Administration}{%
  Nginx, Postfix/Dovecot, Xen Server, Iptables, OpenVPN, DNSSEC, GRE
}

\cvline{Networking}{%
  CCNA certification
}


\newpage
\hspace{3cm}


\section{Communication skills}

\cvlanguage{French}{%
  \textbf{Native tongue}
}{}

\cvlanguage{English}{%
  \textbf{Written, spoken and oral comprehension}
}{Toeic 870/990}

\cvlanguage{German}{%
  \textbf{Basic knowledge}
}{}

\cvlanguage{Japanese}{%
  \textbf{Basic knowledge}
}{}


\section{Personal}

\cvline{Reading}{%
  Classic \& Science-Fiction books
}

\cvline{Movies}{%
  Movies \& series in English, Science-Fiction
}

\cvline{Electronics}{%
  Microprocessor programming, robotics
}

\cvline{RC Hobby}{%
  Flying a quadcopter
}
\cvline{Sport}{Archery}

\end{document}
